\documentclass[11pt,a4paper,sans]{moderncv}

\moderncvtheme[blue]{classic}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.96]{geometry}

\name{Michael}{Heath}
\title{Cloud Architect}
\email{mlheath@outlook.com}

\begin{document}

\makecvtitle
\vspace{-3em}

\section{Professional Experience}
\cventry{2023 -- 2024}{\textbf{Senior Cloud Architect}}{IBM}{CIO Hybrid Cloud}{}{
    \begin{itemize}
        \item Designed and implemented automated enterprise platform solutions for company-wide applications.
        \item Automated containerized VM image builds using OpenShift Virtualization and Tekton.
        \item Built custom operators to manage one of the largest OpenShift Virtualization instances in production.
        \item Integrated new solutions with existing tools through custom code, collaboration, and automation.
        \item Architected automation for logging, vulnerability management, ITSS, backups, and asset auditing.
        \item Planned and implemented architecture for automated OpenShift deployment on IBM Power mainframes.
    \end{itemize}
}

\cventry{2020 -- 2023}{\textbf{Site Reliability Engineer}}{IBM}{CIO Hybrid Cloud}{}{
    \begin{itemize}
        \item Deployed prototype for CIO's primary OpenShift-based application modernization solution.
        \item Automated OpenShift deployments and services using modern techniques on legacy IBM Cloud stacks.
        \item Deployed, managed, and automated OpenShift solutions for storage, backups, networking, and security.
        \item Consulted on custom OpenShift and IBM Cloud infrastructure solutions for platform consumers.
        \item Prototyped automated bare metal OpenShift deployments in CIO data centers.
    \end{itemize}
}

\cventry{2014 -- 2020}{\textbf{Senior Systems Administrator}}{Gila LLC}{}{}{
    \begin{itemize}
        \item Managed VMware ESXi cluster, SAN arrays, and network fabrics adhering to industry standards.
        \item Administered compute, storage, and networking in OVH, Rackspace, and Azure cloud environments.
        \item Migrated file shares to Isilon NAS, relieving SAN and maintaining service continuity.
        \item Oversaw DNS, load balancing, reverse proxies, security audits, pen testing, and compliance audits.
        \item Deployed monitoring solutions (Snort, Graylog, Zabbix) and application stack (JBoss, Apache, MSSQL).
        \item Designed network layouts, including VPN tunnels, DMZs, routing, and ACL management.
        \item Built Kubernetes lab using Foreman and Ansible AWX for CI/CD pipeline testing.
    \end{itemize}
}

\cventry{2013 -- 2014}{\textbf{IT Helpdesk Administrator}}{Gila LLC}{}{}{
    \begin{itemize}
        \item Implemented SCCM for system imaging, inventory, and update management.
        \item Established procedures for employee onboarding, permission management, and offboarding.
        \item Automated processes for new hires, transfers, and terminations.
        \item Troubleshot applications, phones, and systems for 400+ local and remote employees.
        \item Managed and remediated Active Directory, GPOs, DNS, and DHCP settings.
    \end{itemize}
}

\cventry{2011 -- 2013}{\textbf{Operations Support Specialist}}{Gila LLC}{}{}{
    \begin{itemize}
        \item Developed automated processes for client query responses and document management.
        \item Built systems for client query inventory and department efficiency reporting.
        \item Deployed tools for managing and automating inbound document formatting.
    \end{itemize}
}

\vspace{-0.5em}
\section{Technical Skills}
\cvitem{Infrastructure Automation}{\textit{Ansible, Terraform, Containers (Docker, Podman, CRI-O), OpenShift, Velero, Ceph, Packer, Helm, Kustomize, CoreOS}} % Use italics for emphasis
\cvitemwithcomment{Programming Languages}{\textit{Golang, Python, C}}{}
\cvitemwithcomment{Code Pipeline Automation}{\textit{ArgoCD, Tekton, Travis, Jenkins}}{}
\cvitemwithcomment{Agile}{\textit{GitOps, Scrum, Kanban, Jira, ZenDesk}}{}
\cvitemwithcomment{Network Management}{\textit{Juniper, HAProxy, NGINX, Palo Alto, PowerDNS, CoreDNS}}{}

\vspace{-0.5em}
\section{Education}
\cventry{Aug 2017}{Bachelor of Science in Computer Science}{Texas State University}{San Marcos, TX}{\textit{}}{Minor: Mathematics}

\cventry{May 2013}{Associate of Science: General Engineering}{Austin Community College}{Austin, TX}{\textit{}}{}

\end{document}