\documentclass[letterpaper]{article}
\usepackage[margin=0.25in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{color}
\setlist[itemize]{nosep}

% Personal Information
\def\name{Michael Heath}
\def\phone{512-419-8804}
\def\email{mlheath@outlook.com}

\begin{document}

\begin{center}
    {\huge\textbf{\name}}\\
    {\small\phone \\ \email}
\end{center}

\textcolor{blue}{\rule{\linewidth}{1pt}}

\vspace{0.5em}
\begin{minipage}{\dimexpr\textwidth-1in\relax}
    \section*{Experience}
    \begin{itemize}
        \item Senior Cloud Architect, IBM, Austin - TX, Jan 2023 -- Apr 2024
        \begin{itemize}
            \item Designed and implemented automated enterprise platform solutions for company-wide applications.
            \item Automated containerized VM image builds using Ansible, Packer, OpenShift Virtualization, and Tekton.
            \item Built custom operators to manage one of the largest OpenShift Virtualization instances in production.
            \item Integrated new solutions with existing tools through custom code, collaboration, and automation.
            \item Architected automation for logging, vulnerability management, ITSS, backups, and asset auditing.
            \item Planned and implemented architecture for automated OpenShift deployment on IBM Power mainframes. \\
        \end{itemize}
    \end{itemize}

\begin{itemize}
    \item Site Reliability Engineer, IBM, Austin - TX, Jan 2019 -- Dec 2023
    \begin{itemize}
        \item Deployed prototype for CIO's primary OpenShift-based application modernization solution.
        \item Automated OpenShift deployments and services using modern techniques on legacy IBM Cloud stacks.
        \item Deployed, managed, and automated OpenShift solutions for storage, backups, networking, and security.
        \item Consulted on custom OpenShift and IBM Cloud infrastructure solutions for platform consumers.
        \item Piloted KubeVirt golden image pipeline utilizing Packer, Ansible, and Travis allowing for VM images to be built anywhere. 
        \item Prototyped automated bare metal OpenShift deployments in CIO data centers. \\
    \end{itemize}
\end{itemize}

\begin{itemize}
    \item Senior Systems Administrator, Gila LLC, Austin - TX, Mar 2014 -- Dec 2020
    \begin{itemize}
        \item Managed VMware ESXi cluster, SAN arrays, and network fabrics adhering to industry standards.
        \item Administered compute, storage, and networking in OVH, Rackspace, and Azure cloud environments.
        \item Migrated file shares to Isilon NAS, relieving SAN and maintaining service continuity.
        \item Oversaw DNS, load balancing, reverse proxies, security audits, pen testing, and compliance audits.
        \item Deployed monitoring solutions (Snort, Graylog, Zabbix) and application stack (JBoss, Apache, MSSQL).
        \item Designed network layouts, including VPN tunnels, DMZs, routing, and ACL management.
        \item Built Kubernetes lab using Foreman and Ansible AWX for CI/CD pipeline testing. \\
    \end{itemize}
\end{itemize}

\begin{itemize}
    \item IT Helpdesk Administrator, Gila LLC, Austin - TX, Jun 2013 -- Mar 2014
    \begin{itemize}
        \item Implemented SCCM for system imaging, inventory, and update management, minimizing IT Helpdesk workload.
        \item Established automated procedures for employee onboarding, permission management, and offboarding.
        \item Troubleshot applications, phones, and systems for 400+ local and remote employees.
        \item Managed and remediated Active Directory, GPOs, DNS, and DHCP settings \\
    \end{itemize}
\end{itemize}

\begin{itemize}
    \item Operations Support Specialist, Gila LLC, Austin - TX, Mar 2011 -- Jun 2013
    \begin{itemize}
        \item Developed automated processes for client query responses and document management.
        \item Built systems for client query inventory and department efficiency reporting.
        \item Deployed tools for managing and automating inbound document formatting.
    \end{itemize}
\end{itemize}
\end{minipage}

\vspace{0.5em}

\textcolor{blue}{\rule{\linewidth}{1pt}}

\vspace{0.5em}
\begin{minipage}{\dimexpr\textwidth-1in\relax}
\section*{Education}
\begin{itemize}
    \item Bachelor of Science, Computer Science - Math Minor, Texas State University, 2017
    \item Associate of Science, General Engineering, Austin Community College, 2013
\end{itemize}
\end{minipage}
\vspace{0.5em}

\textcolor{blue}{\rule{\linewidth}{1pt}}

\vspace{0.5em}

\begin{minipage}{\dimexpr\textwidth-1in\relax}
\section*{Technical Skills}
\hspace{0.25in}
\begin{tabularx}{\textwidth}{@{}X@{\hskip\tabcolsep}X@{}}
\textbf{Agile} & \textbf{Code Pipeline Automation}\\
GitOps, Scrum, Kanban, Jira, ZenDesk & ArgoCD, Tekton, Travis, Jenkins\\
\textbf{Programming Languages} &  \textbf{Network Management}\\
Golang, Python, C & Juniper, HAProxy, NGINX, PaloAlto, PowerDNS, CoreDNS \\
\textbf{Infrastructure Automation} & \textbf{Infrastructure Monitoring}\\
Ansible, Terraform, Containers (Docker, Podman, CRI-O), OpenShift, Velero, Ceph, Packer, Helm, Kustomize, CoreOS & Prometheus, Grafana, Zabbix, Instana, Dynatrace
\end{tabularx}
\end{minipage}


\end{document}